---
title: "DM Project"
author: "Louise Cazalet and Esteban Marianadin"
format: html
editor: visual
---

# Project Title

#### Louise Cazalet-Dance & Esteban Marianadin

**Link to our Github project :** https://github.com/esteban-mrnd/dm-project.git

### Links to the data sources

All the following links include the filters we used to get the data for our analysis.

rajouter les liens

### Description of the sources (?)

on peut réorganiser pour faire variable par variable ?

### Short description of the project

### Data Import

```{r}
library(vroom)
library(here)
library(dplyr)
library(tidyr)
library
here::i_am("dm-project.Rproj")
```

```{r}
patents <- vroom(here("data","patents.csv"))
gdp_regions <- vroom(here("data","gdp_regions.csv"))
precipitation <- vroom(here("data","extreme_precipitations.csv"))
health_risks <- vroom(here("data","health_risks.csv"))
heat_stress <- vroom(here("data","heat_stress.csv"))
wildfires <- vroom(here("data","wildfires.csv"))
rd_exp_country <- vroom(here("data","rd-exp-country.csv"))

```

### Data description

```{r}
summarize_data <- function(df) {
  df |> summarize(
    `Number of lines` = n(),
    `Number of columns` = ncol(df),
    start_year = min(df[["TIME_PERIOD"]], na.rm = TRUE),
    end_year   = max(df[["TIME_PERIOD"]], na.rm = TRUE)
  )
}


summarize_data(patents)
summarize_data(gdp_regions)
summarize_data(precipitation)
summarize_data(health_risks)
summarize_data(heat_stress)
summarize_data(wildfires)
```


### Key Variable : share of green patent


#### Clean patents and create final database

```{r}
df_final <- patents |>
  select(REF_AREA,`Zone de référence`, TIME_PERIOD, COUNTRY, Pays, OBS_VALUE, `Sélection de domaines technologiques de l'OCDE`)


df <- df_final|>
  pivot_wider(
    names_from = `Sélection de domaines technologiques de l'OCDE`,
    values_from = OBS_VALUE
  )


df_complete <- df 

```











